Sperm should evolve to make female meiosis fair.

### 2014-07-28 writeup_and_notes/GeneticsResub/reviews.tex
yb minor changes for response on  7/28 (again)

\item
\begin{singlespace}
I did not feel that the authors made a convincing case that this is an
important phenomenon in its own right.  P. 5 has one short paragraph pointing to
what seems like some rather indirect evidence of male influence on drive.
Consequently, I find myself wondering whether this manuscript addresses a topic
of sufficient importance for Genetics.  The authors do make an interesting
prediction regarding drive effects in hybrids but in the absence of any current
evidence it is hard to know whether this is just an interesting idea that never
really happens. \\
\end{singlespace}

@@

\begin{singlespace}
\item	 \emph{Finally, female meiotic drive potentially can be suppressed by alleles
expressed in the female (traditional models) or by alleles originating in the
sperm and acting in the egg immediately after fertilization (the authors new
model).  It would be useful to compare the constraints for the evolution of both
types of suppressors to evaluate if sperm-mediated suppression of female meiosis
has some evolutionary advantage that make it easier to evolve or non-redundant
to female-coded suppressors. }
\end{singlespace}
\begin{singlespace}
	{\bf{Response -- }}  For comparison, we have added a female meiotic drive suppressor unlinked to a driver as model 
	$6^\prime$, and compared its evolution to a sperm acting driver.
	In general, the spread of an unlinked female drive suppressor is qualitatively similar to that of an unlinked sperm-acting drive suppressor; 
	however, the initial spread of the sperm suppressor is equal to (when the female suppressor is dominant), or more rapid than (otherwise) the female suppressor. 
	Given the difference in mechanism of female drive suppression in sperm as compared to females, sperm suppression of female drive is likely not functionally redundant with female drive suppression and provides a qualitatively different mechanism of suppression.
\end{singlespace}

@@

\begin{singlespace}
\item \emph{There are 6 models described in the text but these are not described in any
detail until the Appendix.  The authors might consider placing a table in the
main body of the text that tersely describes the 6 models? \\ \\}
{\bf{Response -- }} We have added a Methods section, which introduces these six models, and makes our manuscript more in line with the GENETICS format.
\end{singlespace}

>>>>

\item
\begin{singlespace}
\emph{I did not feel that the authors made a convincing case that this is an
important phenomenon in its own right.  P. 5 has one short paragraph pointing to
what seems like some rather indirect evidence of male influence on drive.
Consequently, I find myself wondering whether this manuscript addresses a topic
of sufficient importance for Genetics.  The authors do make an interesting
prediction regarding drive effects in hybrids but in the absence of any current
evidence it is hard to know whether this is just an interesting idea that never
really happens.} \\
\end{singlespace}

@@

\begin{singlespace}
\item	 \emph{Finally, female meiotic drive potentially can be suppressed by alleles
expressed in the female (traditional models) or by alleles originating in the
sperm and acting in the egg immediately after fertilization (the authors new
model).  It would be useful to compare the constraints for the evolution of both
types of suppressors to evaluate if sperm-mediated suppression of female meiosis
has some evolutionary advantage that make it easier to evolve or non-redundant
to female-coded suppressors. }
\end{singlespace}
\begin{singlespace}
	{\bf{Response -- }}  For comparison, we have added a female meiotic drive suppressor unlinked to a driver as model 
	$6^\prime$, and compared its evolution to a sperm acting driver.
	In general, the spread of an unlinked female drive suppressor is qualitatively similar to that of an unlinked sperm-acting drive suppressor; 
	however, the initial spread of the sperm suppressor is equal to (when the female suppressor is dominant), or more rapid (otherwise) than the female suppressor. 
	Given the difference in mechanism of female drive suppression in sperm as compared to females, sperm suppression of female drive is likely not functionally redundant with female drive suppression and provides a qualitatively different mechanism of suppression.
\end{singlespace}

@@

\begin{singlespace}
\item \emph{There are 6 models described in the text but these are not described in any
detail until the Appendix.  The authors might consider placing a table in the
main body of the text that tersely describes the 6 models? \\ \\}
{\bf{Response -- }} We have added a Methods section, which introduces these six models (+ model 6$^\prime$), and makes our manuscript more in line with the GENETICS format.
\end{singlespace}
